---
title: "Readme"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Kenometrics

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/pointonjoel/Kenometrics/branch/master/graph/badge.svg)](https://codecov.io/gh/pointonjoel/Kenometrics?branch=master)
<!-- badges: end -->

The goal of Kenometrics is to provide a set of functions which allow econometrics students to simply conduct important manipulations and tests.

## Installation

You can install the released version of Kenometrics from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("Kenometrics")
```
To install the latest development version from GitHub:
``` r
install.packages("remotes")
remotes::install_github("pointonjoel/Kenometrics")
```
## Overview

The Kenometrics package enables lecturers and students to teach and implement fundemental econometric techniques. Below is a summary of the functions on offer and how they can be used:
<body>
  <ul>
    <li>
      <b>get\_data()</b> 
      <i>A single function to find and source data from a variety of sources (Wooldridge, FRED, txt, Excel)</i></li>
    <li>
      <b>ttest()</b> 
      <i>Conduct a t-test (with a specific hypothesised mean, not necessarily 0)</i></li>
    <li>
      <b>make\_ts()</b>
      <i>Make the data time-series (to allow for lagged variables etc.)</i></li>
    <li>
      <b>chow()</b>
      <i>Conduct a chow test (it adds an intercept and dummy slope and tests the significance depending on if one is testing for a break in the intercept, slope or both)</i></li>
    <li>
      <b>ADF()</b>
      <i>Conduct an ADF test (and if the data are non stationary, it adds the first-difference to the data frame)</i></li>
    <li>
      <b>LRM()</b>
      <i>Find and test the significance of the long run multiplier</i></li>
  </ul>
</body>

The Kenometrics package takes many existing packages and incorporates them as dependencies, simplifying the existing functions they provide. Dependencies include, but are not limited to: wooldridge, zoo, dynlm, fredr, readxl and tseries. Having all of these bundled into one package and harnessed for econometrics means that students can quickly begin putting theory into practice. Without Kenometrics, testing for non-stationary data, for example, can be long-winded and and require multiple packages. However, Kenometrics similifies the code into one line and includes all other necessary packages. Although, students are encouraged to look into the code, which is written in a simple and intuitive way, to see how they could complete the data manipulations without Kenometrics.

## Importing data
When importing data, students may often be overwhelmed with the specifics needed when importing from a variety of sources. The having one function complete with FRED and Excel integration simplies things further. 

To import data to the current environment, there are two ways depending on the type of data. It is reccomended that users also import the [wooldridge package](https://cran.r-project.org/web/packages/wooldridge/index.html), which contains all of the [datasets used in the textbook's examples](https://www.cengage.com/cgi-wadsworth/course_products_wp.pl?fid=M20b&product_isbn_issn=9781111531041):

```{r hseinv}
library(Kenometrics)
library(wooldridge)
data(hseinv)
#Then the dataset can be previewed (and manipulated)
head(hseinv)
```

Kenometrics provides support for a variety of other types of datasets. Simply specify the name of the file/dataset and the type of data.

```{r nasa}
#Code needed to obtain the NASA file on the user's computer
file = system.file("extdata", "NASA.xlsx", package="Kenometrics")
my_wd =substr(file,0,nchar(file)-nchar("NASA.xlsx")-1)
#Once the working directory has been obtained, the get_data function can be used
NASA_data <- get_data("NASA", type="excel", file_loc = my_wd)
print(NASA_data)
```

Whilst the function defaults the working directory to the current location of the workspace, students are encouraged to set a working directory prior to sourcing data. This can be done by using:

```{r setwd}
my_wd="C:/Documents"
#And then for usage
#setwd(my_wd)
```

Note the use of "/" rather than "\", as is customary in R.

Students can also import files from FRED using Kenometrics, once they have obtained a [FRED API key](https://research.stlouisfed.org/docs/api/api_key.html), which is simple and free. For examples, see:

```{r help, results = FALSE}
?get_data
```

## T-tests

Once data has been imported, a t-test can then be conducted. Ordinarily, this is possible through the completing a linear regression and finding the summary of it.

```{r}
simple_model <- lm(lprice ~ lpop + linvpc , data=hseinv)
summary(simple_model)
```

However, this assumes that the hypothesised population mean is 0; there is no scope to change it. To conduct a T-Test where there is a non-0 population mean is simple with Kenometrics:

```{r}
#t_stat <- ttest("linvpc", some_data, "simple_model", pop_mean = -1)
#print(t_stat)
```




```{r chow}
chow(1960, "year", hseinv, "linvpc ~ lpop", "both")
```

```{r delim}
file = system.file("extdata", "sample_data_hseinv.txt", package="Kenometrics")
#data <- read.delim(file)
#data <- make_ts("year", data)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. 
#codecov(token = "7362364f-d882-438c-8156-339b77b22474")

#finsih unit testing
#check the examples above which are commented out
#make LRM function, use roxygen skeleton, add to README, run unit testing.
